Providing a Unified Software Environment for Canada’s National Advanced Computing Centers

### 2019-03-26 paper.tex
Added two figures

\textbf{TODO: Insert figure representing the CVMFS structure of strata. }
\label{fig:CVMFS_structure}

@@

\textbf{TODO: INSERT FIGURE representing our workflow (build => test locally => dev => test on cluster => prod) }
\label{fig:Workflow}

>>>>

\begin{figure}
  \includegraphics[width=0.45\textwidth]{CVMFS-structure.pdf}
  \caption{Diagram of the CVMFS structure. Arrows represent the flow of data. Data is pushed into the stratum-0, but is then fetched by the following layers.}
  \label{fig:CVMFS_structure}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Software-installation-workflow.pdf}
  \caption{Workflow followed by our software installers. At each step, there is a checkpoint to test if the software package works properly.}
  \label{fig:Workflow}
\end{figure}
